Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-16 eswc-2012/phdsymp.tex
start on punchline
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@98 43ef1190-90fd-4dd7-a769-d0121f02b80e
coefficients and stuff
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@99 43ef1190-90fd-4dd7-a769-d0121f02b80e

>>>>

With this analysis, I speculate based on superficial experience that
certain estimated coefficients can be exposed in the service
description to give federated query engines what they need to optimize
for performance characteristics of certain SPARQL
implementations. Adjusting how different features are weighed will
help those who know details of their expected SPARQL use and
normalization-techniques of the weights will answer the special case
of ``the best general-purpose SPARQL engine''.
